---
output:
  pdf_document: default
  date: "18 October 2017"
  html_document: default
  author: "John Beal"
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
require(dplyr)
require(reshape2)
```

```{r BERD by Industry, echo = FALSE}
## http://www.stats.govt.nz/infoshare/
## Research and Development Survey (RAD)
## Table: Total research and development expenditure by industry (Annual-Jun) 
## R & D Industry Split: all non-total industry lines; Time: 2008, 2010, 2012, 2014, 2016
## Downloaded: 17 October 2017 7 am Last Updated: 29 March 2017 10:45 am
BERD_industry <- read.csv(file = "RAD522801_20171017_065838_61.csv", 
                          skip = 1, header = TRUE, check.names = TRUE, nrow = 5, na.strings = "..")
colnames(BERD_industry)[1] <- "Year"
```

```{r BERD by Industry Group, echo = FALSE}
## http://www.stats.govt.nz/infoshare/
## Research and Development Survey (RAD)
## Table: Total research and development expenditure by industry (Annual-Jun) 
## R & D Industry Split: Primary Total, Manufacturing Total, Services Total; Time: 2008, 2010, 2012, 2014, 2016
## Downloaded: 17 October 2017 8:30 am Last Updated: 29 March 2017 10:45 am
BERD_industry_group <- read.csv(file = "RAD522801_20171017_082358_86.csv", 
                          skip = 1, header = TRUE, check.names = TRUE, nrow = 5, na.strings = "..")
colnames(BERD_industry_group)[1] <- "Year"
```


```{r BERD %GDP OECD, echo = FALSE}
## https://stats.oecd.org/Index.aspx?DataSetCode=MSTI_PUB
## OECD Main Scince and Technology Indicators (MSTI)
## BERD as a percentage of GDP
## Downloaded: 17 October 2017 2:30 pm
BERD_GDP <- read.csv(file = "MSTI_PUB_17102017015101164.csv")
```


```{r BERD by Industry Group (GDP)}
## Add column for total BERD by year
BERD_industry_group[ , "Total"] <- summarise(group_by(melt(BERD_industry_group, id.vars = "Year"), Year), 
                                             Total = sum(value))[ , "Total"]

## Append BERD as %GDP from OECD dataset (Note: figure don't match Stats NZ, switching to Stats NZ revised figures)
##BERD_industry_group[ , "%GDP"] <- mutate(filter(BERD_GDP, Country == "New Zealand", YEAR > 2006), 
##                                         Value = round(Value, 2))[ , "Value"]

## BERD as %GDP (revised were available) was taken from the series of Stats NZ Research and Development Surveys
## Each individual survey contains only the figures from the current and previous period
BERD_industry_group[ , "%GDP"] <- c(0.51, 0.51, 0.57, 0.54, 0.64)

```

```{r Future Expectations}
## http://www.stats.govt.nz/infoshare/
## Research and Development Survey (RAD)
## Table: Businesses expectations of own firm's research and development for the next year (Annual-Jun) 
## R & D Industry Split: All; Time: 2016
## Downloaded: 18 October 2017 11:30 pm Last Updated: 29 March 2017 10:45 am 

RDExpectations_2016 <- read.csv(file = "RAD523801_20171018_113944_29.csv", skip = 2, header = TRUE, 
                                check.names = TRUE, nrow = 5, na.strings = "..")
names(RDExpectations_2016)[1] <- "Response"

## R & D Industry Split: All; Time: 2014
## Downloaded: 18 October 2017 12 am Last Updated: 29 March 2017 10:45 am 
RDExpectations_2014 <- read.csv(file = "RAD523801_20171018_115604_12.csv", skip = 2, header = TRUE, 
                                check.names = TRUE, nrow = 5, na.strings = "..")
names(RDExpectations_2014)[1] <- "Response"
```


Minister of Science and Innovation

#New Zealand's progress towards increasing Business Expenditure on Research and Development (BERD)

##Purpose

The purpose of this briefing is to update you on the progress towards the goal of increasing Business Expenditure on Research and Development (BERD) to 1% of GDP by 2018. 

##Introduction

In 2015, as part of the *National Statement of Science Investment 2015-2025*, the government set the aspirational goal of increasing New Zealand's BERD to 1% of GDP by 2018.This is part of longer term objective of increasing New Zealand's BERD to well above 1% of GDP by 2025 and promoting a thriving independent research sector.

BERD is a measure of Research and Development (R & D) activities *performed* in the business sector. The expenditure on R & D activities can include funding from sources other than the businesses' own investment e.g. government grants administered by Callaghan Innovation. BERD does not include R & D expenditure on behalf of businesses conducted in universities or government institutions e.g. Crown Research Institutes (CRIs).

Increasing BERD is critically important to improving New Zealand's economy. This is because of the important role BERD plays in innovation, and the development of new products and improved production techniques. Increasing BERD will support the economy's long term productivity and New Zealand's international competitiveness. New Zealand's level of BERD, although growing, remains low compared to other small advanced countries.   




<!---
BERD includes R & D performed by business, even if the funding is received elsewhere (e.g. government grants). BERD does not include R & D funded by business, but performed by government or higher educational institutions.
-->

  


##Progress to Date


BERD in New Zealand is measured by Statistics New Zealand in the two-yearly Research and Development Survey. The most recent survey was for 2016 and the results were released in March 2017. The next  survey is scheduled for 2018 and the results are expected to be released in April 2019.

BERD in terms of expenditure and as a percentage of GDP for the period 2008 - 2016 is shown in the graph below. The expenditure on R & D is broken down to show the contribution of the primary, manufacturing and services industry sectors. Since 2008, BERD has grown from `r select(filter(BERD_industry_group, Year == 2008), "%GDP")`% to `r select(filter(BERD_industry_group, Year == 2016), "%GDP")`% of GDP. As can be noted for the period 2012 - 2014, BERD can *increase* in dollar terms (from $`r prettyNum(select(filter(BERD_industry_group, Year == 2012), Total), big.mark = ",")` million to $`r prettyNum(select(filter(BERD_industry_group, Year == 2014), Total), big.mark = ",")` million), but still *decrease* as a percentage of GDP (from `r select(filter(BERD_industry_group, Year == 2012), "%GDP")`% to `r select(filter(BERD_industry_group, Year == 2014), "%GDP")`% of GDP) if the growth in expenditure is not as rapid as the growth in GDP over the period. 

The services sector has had the largest increase in R & D expenditure over the eight year period from 2008, up $`r prettyNum((select(filter(BERD_industry_group, Year == 2016), Services.total)-select(filter(BERD_industry_group, Year == 2008), Services.total)))` million to $`r prettyNum(select(filter(BERD_industry_group, Year == 2016), Services.total), big.mark = ",")` million (`r round(((select(filter(BERD_industry_group, Year == 2016), Services.total)-select(filter(BERD_industry_group, Year == 2008), Services.total))/select(filter(BERD_industry_group, Year == 2008), Services.total))*100, 0)`%). The manufacturing sector expenditure increased  $`r prettyNum((select(filter(BERD_industry_group, Year == 2016), Manufacturing.total)-select(filter(BERD_industry_group, Year == 2008), Manufacturing.total)))` million to $`r prettyNum(select(filter(BERD_industry_group, Year == 2016), Manufacturing.total), big.mark = ",")` million (`r round(((select(filter(BERD_industry_group, Year == 2016), Manufacturing.total)-select(filter(BERD_industry_group, Year == 2008), Manufacturing.total))/select(filter(BERD_industry_group, Year == 2008), Manufacturing.total))*100, 0)`%) and the primary industries sector showed the smallest overall increase, up $`r prettyNum((select(filter(BERD_industry_group, Year == 2016), Primary.total)-select(filter(BERD_industry_group, Year == 2008), Primary.total)))` million to $`r prettyNum(select(filter(BERD_industry_group, Year == 2016), Primary.total), big.mark = ",")` million (`r round(((select(filter(BERD_industry_group, Year == 2016), Primary.total)-select(filter(BERD_industry_group, Year == 2008), Primary.total))/select(filter(BERD_industry_group, Year == 2008), Primary.total))*100, 0)`%).

It is recognised in the *National Statent of Science Investment* that New Zealand's primary industries are characterised by a large number of small producers making the same product, meaning that investment by individual firms in R & D is often uneconomic. This has been addressed historically by R & D for these producers being undertaken in Crown Research Institutes (CRIs) and universities - and therefore this expenditure is not counted statistically as BERD.





```{r Plot_BERD, message = FALSE, warning= FALSE, eval = FALSE, echo = FALSE}
require(ggplot2)
require(reshape2)
require(ggthemes)
BERD_industry_melt <- melt(BERD_industry, id.vars = "Year")
names(BERD_industry_melt)[2] <- "Industry"
BERDplot <- ggplot(data = BERD_industry_melt,aes(y = value, x = Year, fill = Industry)) + 
                    theme_economist() +
                    geom_bar(stat = "identity") +
                    ylab("$(million)") + scale_x_continuous(breaks = seq(2008, 2016, 2), name = "")
plot(BERDplot)
```


```{r Plot_BERD_group, echo = FALSE, message = FALSE}
require(ggplot2)
require(ggthemes)
require(reshape2)

BERD_industry_group_melt <- melt(BERD_industry_group, id.vars = "Year")
names(BERD_industry_group_melt)[2] <- "Industry"
BERDplot_group <- ggplot(data = BERD_industry_group_melt,aes(y = value, x = Year, fill = Industry)) + 
                    geom_bar(data = subset(BERD_industry_group_melt, 
                            Industry %in% c("Primary.total", "Manufacturing.total", "Services.total")), 
                            stat = "identity") + 
                    theme_economist() +
                    theme(axis.title.y = element_text(angle = 0, vjust = 1),
                          axis.text.y = element_text(hjust = 1),
                          plot.subtitle = element_text(size = 15, hjust = 0.5),
                          plot.caption = element_text(hjust = 0)) +
                    scale_fill_economist(name = "",
                                    labels = c("Primary (total)", "Manufacturing (total)", "Services (total)", "")) +
                    scale_x_continuous(breaks = seq(2008, 2016, 2), name = "") +
                    scale_y_continuous(labels = scales::comma, limits = c(0, 2000)) +
                    ggtitle("Business expenditure on research and development", subtitle = "By industry") +
                    labs(y = "$(million)", 
                         caption = "Source: Stats NZ     (Figures in parentheses give BERD as a percentage of GDP)") +
                    geom_text(data = subset(BERD_industry_group_melt, Industry == "%GDP"), 
                              aes(x = Year, y = 1750,label = paste("(", value, ")")), 
                              show.legend = FALSE, inherit.aes = FALSE)
plot(BERDplot_group)
```

### 2016 Research and Development Survey findings

Focusing on the findings from the most recent survey, 2016 BERD has increased by $`r select(filter(BERD_industry_group, Year == 2016), Total) - select(filter(BERD_industry_group, Year == 2014), Total)` million since 2014 to reach $`r prettyNum(select(filter(BERD_industry_group, Year == 2016), Total), big.mark = "," )` million.

The services grouping had the largest increase in R & D expenditure, up $`r select(filter(BERD_industry_group, Year == 2016), Services.total) - select(filter(BERD_industry_group, Year == 2014), Services.total)` million to $`r select(filter(BERD_industry_group, Year == 2016), Services.total)` million. Within the services grouping, the computer services industry, which includes software production and web design, had the largest growth, up $`r select(filter(BERD_industry, Year == 2016), Computer.services) - select(filter(BERD_industry, Year == 2014), Computer.services)` million (`r round(((select(filter(BERD_industry, Year == 2016), Computer.services) - select(filter(BERD_industry, Year == 2014), Computer.services))/select(filter(BERD_industry, Year == 2014), Computer.services)*100), 0) `%) since 2014.    

The manufacturing sector expenditure increased  $`r prettyNum((select(filter(BERD_industry_group, Year == 2016), Manufacturing.total)-select(filter(BERD_industry_group, Year == 2014), Manufacturing.total)))` million since 2014 to $`r prettyNum(select(filter(BERD_industry_group, Year == 2016), Manufacturing.total), big.mark = ",")` million (`r round(((select(filter(BERD_industry_group, Year == 2016), Manufacturing.total)-select(filter(BERD_industry_group, Year == 2014), Manufacturing.total))/select(filter(BERD_industry_group, Year == 2014), Manufacturing.total))*100, 0)`%), while primary industries expenditure increased only marginally, up  $`r prettyNum((select(filter(BERD_industry_group, Year == 2016), Primary.total)-select(filter(BERD_industry_group, Year == 2014), Primary.total)))` million since 2014 to $`r prettyNum(select(filter(BERD_industry_group, Year == 2016), Primary.total), big.mark = ",")` million (`r round(((select(filter(BERD_industry_group, Year == 2016), Primary.total)-select(filter(BERD_industry_group, Year == 2014), Primary.total))/select(filter(BERD_industry_group, Year == 2014), Primary.total))*100, 0)`%)  

In the 2016 survey, a total of `r sum(select(filter(RDExpectations_2016, Response %in% c("Increase", "Stay the same")), Business.sector.total))`% of businesses undertaking R & D expected their expenditure on R & D in the next year to either rise or stay the same, up from `r sum(select(filter(RDExpectations_2014, Response %in% c("Increase", "Stay the same")), Business.sector.total))`% in 2014. The computer services industry was the most positive about future R & D expenditure, with `r sum(select(filter(RDExpectations_2016, Response == "Increase"), Computer.services))`% of businesses anticipating to increase their R & D expenditure in the next year. 

```{r Plot_RDIntentions, message = FALSE, warning= FALSE, eval = FALSE, echo = FALSE}
require(ggplot2)
require(ggthemes)
require(reshape2)

df <- select(filter(melt(RDExpectations_2016), variable == "Business.sector.total"), X., value)
names(df) <- c("Response", "%")

Plot_RDintentions <-  ggplot(data = df, 
                             aes(x = "", y = "%", fill = Response)) +
                      geom_bar(stat = "identity") +
                      theme_economist()
plot(Plot_RDintentions)
```


##Conclusion

New Zealand's BERD has grown by $`r prettyNum((select(filter(BERD_industry_group, Year == 2016), Total)-select(filter(BERD_industry_group, Year == 2008), Total)))` million or `r round((select(filter(BERD_industry_group, Year == 2016), "%GDP")-select(filter(BERD_industry_group, Year == 2008), "%GDP")), 2)` percentage points of GDP between 2008 and 2016, with the biggest increase occurring between 2014 and 2016. The services sector made the largest contribution to increasing BERD, and the computer services industry in particular. Manufacturing made the next largest contribution, while the primary industries sector increased expenditure only marginally. 

Although recent strong growth in BERD has started to close the gap between current levels of BERD and the aspirational goal of 1% GDP, this target is unlikely to be met by the target of 2018. This would require significant growth in BERD over a short time period of two years between 2016 and 2018, at a time when robust economic growth means expenditure must increase in dollar terms to maintain its level in terms of percentage of GDP.

There are high-levels of business confidence in maintaining or increasing expenditure on R & D in 2017 (`r sum(select(filter(RDExpectations_2016, Response %in% c("Increase", "Stay the same")), Business.sector.total))`%) among businesses undertaking R & D, and especially among industries with a track record of strong recent increases in R & D expenditure, such as the computer services industry. This is supportive of further strong increases in BERD in the medium term  towards the target of 1% of GDP. 

##Recommendations

The ministry could perform further analysis on how the leveraging of government expenditure by businesses for co-funded R & D activities (e.g business grants administered by Callaghan Innovation) affects their current and anticipated future R & D investment levels. Particular focus could be given to industries with strong recent growth in BERD, such as the computer services industry. The ministry could provide further advice as to whether there are opportunities for promoting similar increases in R & D expenditure through policy settings in industries with an acknowledged long term lack of BERD (e.g. primary industries).    